% das Papierformat zuerst
\documentclass[a4paper, 12pt]{article}

\usepackage{fancyvrb}
\usepackage{verbatim}
\usepackage[pdftex]{graphicx}
\usepackage{changepage}
\usepackage{ragged2e}

\usepackage[left=30mm,right=35mm,top=25mm,bottom=25mm,showframe=false]{geometry}


% hier beginnt das Dokument
\begin{document}

% =======================================================================
% Titelseite

\thispagestyle{empty}

\begin{flushright}
    \begin{tabular}{r}
        \textbf{Maurice *Name*}
        \\
        \**Street, Number*
        \\
        Germany - *Place*
        \\
        \**mail-address*
        \\
        (+49) *telefone number*
        \\
        \\
        \today
    \end{tabular}
\end{flushright}


\begin{adjustwidth}{-2mm}{}
\begin{flushleft}
    \begin{tabular}{l}
        \textbf{*Company name*}
        \\
        \**Place*
        \\
        \**Street*
        \\
        \**Country*
    \end{tabular}
\end{flushleft}
\end{adjustwidth}

\begin{verbatim}




\end{verbatim}



\justify
Dear Sir or Madam,
\newline
\newline
my name is Maurice \**Name*. I am finishing my masters degree (Msc) in computer science with focus on virtual reality, physics animation
and computergraphics right now.
\newline
\newline
I live in Germany and study computer science in a very renowned university (\**University* - University of applied Sciences).
After visiting \**City* for several weeks a few years back, I decided, that this is the place I want to go. This, combined with \**Company* having its
headquarters in \**City*, finalized my decision of moving to your beautiful city.
\newline
\newline
With several highly relevant projects in the field of computer graphics, as well as experience with various programming languages and the
OpenGL pipeline, I think, I will be a good fit for a position in your computergraphics and development department.
\newline
\newline
My masters degree will be finished in november 2016. After that, I will be visiting \**Country* for a few months before finally moving to
\**City*.
During that time I will be available for personal interviews and meetings. Apart from that, I can arrange telefone/Skype interviews at any time.
Please see a more detailed description of my projects and life in the attachments.
\newline
\newline
I would very much appreciate hearing from you.
\newline
\newline
Yours sincerely,
\newline
\newline
Maurice \**Name*




\end{document}

